An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-02-19 paper.tex

There are some notable gait data sets and databases besides Winter's
authoritative set that are publicly available. The International Society of
Biomechanics has maintained a web page (http://isbweb.org/data) since
approximately 1995 that includes data sets for download and mostly unencumbered
use. For example, the kinematic and force plate measurements from several
subjects from \cite{Vaughan1992} is available on the site. At another website,
the CGA Normative Gait Database, \cite{Kirtley2014} shares normative gait data
from several studies and these files have influenced other studies, for example
the average gait cycles from children used in \cite{Bogert2003}.

>>>>

There are some notable gait data sets and databases besides Winter's
authoritative set that are publicly available. The International Society of
Biomechanics has maintained a web page (http://isbweb.org/data) since
approximately 1995 that includes data sets for download and mostly unencumbered
use. For example, the kinematic and force plate measurements from several
subjects from \cite{Vaughan1992} is available on the site. At another website,
the CGA Normative Gait Database, \cite{Kirtley2014} curates and shares
normative clinical gait data collected from multiple labs and these datasets
have influenced other studies, for example the average gait cycles from
children used in \cite{Bogert2003}.
